Tailoring Differentially Private Bayesian Inference to Distance Between Distributions

### 2018-10-26 Arxiv/main.tex
fix typos

Let $\ux{t} = \ux{r} + k$. The proof is given by cases:
\begin{itemize}
  \item {\boldmath$\ux{r} \neq 0$, $\ux{r} + k \neq 0$}. \todo{$r \in \mathcal{R}_2 \land t \in \mathcal{R}_2$} \\
  By $\ux{r} + k \neq 0$, $\cardinality{\dataobs}{t} = 2$. \todo{By $t \in \mathcal{R}_2$, $\cardinality{\dataobs}{t} = 2$}\\
  By $\ux{r} \neq 0 $, $\cardinality{\dataobs}{r} = 2$. \todo{By $r \in \mathcal{R}_2$, $\cardinality{\dataobs}{r} = 2$}\\
  Destruct k:
  \begin{itemize}
    \item  $k \geq 0$: $\implies$\\
      \begin{equation*}
      \begin{split}
      LHS 
      & = \cardinality{\dataobs}{r} \cdot \hexpmechPr{\dataobs}{z = r}     (Apply\ Lemma\ \ref{lem_score_pro_convert})\\
      & = \cardinality{\dataobs}{r} \cdot \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}} 
      (Apply\ Definition\ \ref{def_smoo})\\
      & = \cardinality{\dataobs}{r} \cdot \frac{exp(\frac{-\epsilon \ux{r}}{2 S(\dataobs)})}{\unomalizer{\dataobs}}
      (Apply\ \ux{r} = \hellinger(\bysinfer(\dataobs), r))\\
      & = 2 \cdot \frac{exp(\frac{-\epsilon \ux{r}}{2 S(\dataobs)})}{\unomalizer{\dataobs}}                  (Apply\ \cardinality{\dataobs}{r} = 2)\\
      & = 2 \cdot \frac{exp(\frac{-\epsilon (\ux{r} + k - k)}{2 S(\dataobs)})}{\unomalizer{\dataobs}}\\
      & = 2 \cdot \frac{exp(\frac{-\epsilon (\ux{r} + k)}{2 S(\dataobs)} + \frac{\epsilon k}{2 S(\dataobs)})}{\unomalizer{\dataobs}}\\
      & = 2 \cdot \frac{exp(\frac{-\epsilon (\ux{r} + k)}{2 S(\dataobs)})}{\unomalizer{\dataobs}} \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}}\\
      & = 2 \cdot \frac{exp(\frac{-\epsilon (\ux{t})}{2 S(\dataobs)})}{\unomalizer{\dataobs}} \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}}  (Apply \ \ux{t} = \ux{r} + k)\\
      & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot 2 \cdot \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs), t)}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}} 
      (Apply\ \ux{r} = \hellinger(\bysinfer(\dataobs), r))\\
      & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot 2 \hexpmechPr{\dataobs}{z = t}       (Apply\ Definition\ \ref{def_smoo})\\
      & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \cardinality{\dataobs}{t} \hexpmechPr{\dataobs}{z = t}         (Apply \ \cardinality{\dataobs}{t} = 2)\\
      & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{\ux{z} = \ux{t}}               (Apply \ Lemma\ \ref{lem_score_pro_convert})\\
      & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{\ux{z} = (\ux{r} + k)}         (Apply \ \ux{t} = \ux{r} + k)\\
      & \leq e^{(\frac{\epsilon k}{2 S(\dataobs)} + \ln 2)} \hexpmechPr{\dataobs}{\ux{z} = (\ux{r} + k)}\\
      & = RHS.
      \end{split}
      \end{equation*}

@@

      \begin{equation*}
      \begin{split}
      LHS 
      & = \cardinality{\dataobs}{r} \cdot \hexpmechPr{\dataobs}{z = r}     (Apply\ Lemma\ \ref{lem_score_pro_convert})\\
      & = \cardinality{\dataobs}{r} \cdot \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}} 
      (Apply\ Definition\ \ref{def_smoo})\\
      & = \cardinality{\dataobs}{r} \cdot \frac{exp(\frac{-\epsilon \ux{r}}{2 S(\dataobs)})}{\unomalizer{\dataobs}}
      (Apply\ \ux{r} = \hellinger(\bysinfer(\dataobs), r))\\
      & = 2 \cdot \frac{exp(\frac{-\epsilon \ux{r}}{2 S(\dataobs)})}{\unomalizer{\dataobs}}                  (Apply\ \cardinality{\dataobs}{r} = 2)\\
      & = 2 \cdot \frac{exp(\frac{-\epsilon (\ux{r} + k - k)}{2 S(\dataobs)})}{\unomalizer{\dataobs}}\\
      & = 2 \cdot \frac{exp(\frac{-\epsilon (\ux{r} + k)}{2 S(\dataobs)} + \frac{\epsilon k}{2 S(\dataobs)})}{\unomalizer{\dataobs}}\\
      & = 2 \cdot \frac{exp(\frac{-\epsilon (\ux{r} + k)}{2 S(\dataobs)})}{\unomalizer{\dataobs}} \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}}\\
      & = 2 \cdot \frac{exp(\frac{-\epsilon (\ux{t})}{2 S(\dataobs)})}{\unomalizer{\dataobs}} \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}}  (Apply \ \ux{t} = \ux{r} + k)\\
      & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot 2 \cdot \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs), t)}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}} 
      (Apply\ \ux{r} = \hellinger(\bysinfer(\dataobs), r))\\
      & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot 2 \hexpmechPr{\dataobs}{z = t}       (Apply\ Definition\ \ref{def_smoo})\\
      & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \cardinality{\dataobs}{t} \hexpmechPr{\dataobs}{z = t}         (Apply \ \cardinality{\dataobs}{t} = 2)\\
      & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{\ux{z} = \ux{t}}               (Apply \ Lemma\ \ref{lem_score_pro_convert})\\
      & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{\ux{z} = (\ux{r} + k)}         (Apply \ \ux{t} = \ux{r} + k)\\
      & \leq e^{(\frac{\epsilon k}{2 S(\dataobs)} + \ln 2)} \hexpmechPr{\dataobs}{\ux{z} = (\ux{r} + k)}\\
      & = RHS.
      \end{split}
      \end{equation*}

@@

  \item {\boldmath$\ux{r} = 0, \ux{r} + k \neq 0$}. \todo{$r \in \mathcal{R}_1 \land t \in \mathcal{R}_2$}\\
        By $\ux{r} = 0$, $\cardinality{\dataobs}{r} = 1$. \todo{By $r \in \mathcal{R}_1$, $\cardinality{\dataobs}{t} = 1$}\\
        By $\ux{r} + k = k \neq 0$, $\cardinality{\dataobs}{t} = 2$. \todo{By $t \in \mathcal{R}_2$, $\cardinality{\dataobs}{t} = 2$}\\
        $\implies$\\
        \begin{equation*}
        \begin{split}
        LHS 
        & = \cardinality{\dataobs}{r} \cdot \hexpmechPr{\dataobs}{z = r}     (Apply\ Lemma\ \ref{lem_score_pro_convert})\\
        & = \cardinality{\dataobs}{r} \cdot \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}} 
        (Apply\ Definition\ \ref{def_smoo})\\
        & = \cardinality{\dataobs}{r} \cdot \frac{exp(\frac{-\epsilon \ux{r}}{2 S(\dataobs)})}{\unomalizer{\dataobs}}
        (Apply\ \ux{r} = \hellinger(\bysinfer(\dataobs), r))\\
        & = \frac{exp(\frac{- \epsilon \ux{r}}{2 S(\dataobs)})}{\unomalizer{\dataobs}}                        (Apply \ \cardinality{\dataobs}{r} = 1) \\
        & = \frac{exp(\frac{- \epsilon (\ux{r} + k - k)}{2 S(\dataobs)})}{\unomalizer{\dataobs}}\\
        & = \frac{exp(\frac{- \epsilon (\ux{r} + k)}{2 S(\dataobs)} + \frac{\epsilon k}{2 S(\dataobs)})}{\unomalizer{\dataobs}}\\
        & = \frac{exp(\frac{-\epsilon (\ux{r} + k)}{2 S(\dataobs)})}{\unomalizer{\dataobs}} \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}}\\
        & = \frac{exp(\frac{-\epsilon (\ux{t})}{2 S(\dataobs)})}{\unomalizer{\dataobs}} \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}}  (Apply \ \ux{t} = \ux{r} + k)\\
        & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs), t)}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}} 
        (Apply\ \ux{r} = \hellinger(\bysinfer(\dataobs), r))\\
        & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{z = t}       (Apply\ Definition\ \ref{def_smoo})\\
        & < 2 \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{z = t}\\
        & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \cardinality{\dataobs}{t} \hexpmechPr{\dataobs}{z = t}   (Apply \ \cardinality{\dataobs}{t} = 2)\\
        & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{\ux{z} = \ux{t}}         (Apply \ Lemma\ \ref{lem_score_pro_convert})\\
        & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{\ux{z} = (\ux{r} + k)}   (Apply \ \ux{t} = \ux{r} + k)\\
        & \leq e^{(\frac{\epsilon k}{2 S(\dataobs)} + \ln 2)} \hexpmechPr{\dataobs}{\ux{z} = ( \ux{r} + k)}\\
        & = RHS.
        \end{split}
        \end{equation*}

@@

      $\implies$
      \begin{equation*}
      \begin{split}
      LHS   
      & = \cardinality{\dataobs}{r} \cdot \hexpmechPr{\dataobs}{z = r}     (Apply\ Lemma\ \ref{lem_score_pro_convert})\\
      & = \cardinality{\dataobs}{r} \cdot \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}} 
      (Apply\ Definition\ \ref{def_smoo})\\
      & = \cardinality{\dataobs}{r} \cdot \frac{exp(\frac{-\epsilon \ux{r}}{2 S(\dataobs)})}{\unomalizer{\dataobs}}
      (Apply\ \ux{r} = \hellinger(\bysinfer(\dataobs), r))\\
      & = 2 \cdot \frac{exp(\frac{-\epsilon \ux{r}}{2 S(\dataobs)})}{\unomalizer{\dataobs}}                  (Apply \ \cardinality{\dataobs}{r} = 2)\\
      & = 2 \cdot \frac{exp(\frac{-\epsilon (\ux{r} + k - k)}{2 S(\dataobs)})}{\unomalizer{\dataobs}}\\
      & = 2 \cdot \frac{exp(\frac{-\epsilon (\ux{r} + k)}{2 S(\dataobs)} + \frac{\epsilon k}{2 S(\dataobs)})}{\unomalizer{\dataobs}}\\
      & = 2 \cdot \frac{exp(\frac{-\epsilon (\ux{r} + k)}{2 S(\dataobs)})}{\unomalizer{\dataobs}} \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}}\\
      & = 2 \cdot \frac{exp(\frac{-\epsilon (\ux{t})}{2 S(\dataobs)})}{\unomalizer{\dataobs}} \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}}  (Apply \ \ux{t} = \ux{r} + k)\\
      & = 2 \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs), t)}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}} 
      (Apply\ \ux{r} = \hellinger(\bysinfer(\dataobs), r))\\
      & = 2 \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}} \hexpmechPr{\dataobs}{z = t}       (Apply\ Definition\ \ref{def_smoo})\\
      & = 2 \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \cardinality{\dataobs}{t} \hexpmechPr{\dataobs}{z = t} (Apply\ \cardinality{\dataobs}{t} = 1)\\
      & = 2 \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{\ux{z} = \ux{t}}       (Apply \ Lemma\ \ref{lem_score_pro_convert})\\
      & = 2 \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{\ux{z} = (\ux{r} + k)} (Apply \ \ux{t} = \ux{r} + k)\\
      & = e^{\ln 2} \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{\ux{z} = (\ux{r} + k)}\\
      & = e^{(\frac{\epsilon k}{2 S(\dataobs)} + \ln 2)} \hexpmechPr{\dataobs}{\ux{z} = (\ux{r} + k)}\\
      & = RHS.
      \end{split}
      \end{equation*}

@@

        \begin{equation*}
        \begin{split}
        LHS 
        & = \hexpmechPr{\dataobs}{\ux{z} = \ux{r} + 0}\\
        & = \hexpmechPr{\dataobs}{\ux{z} = \ux{r} + k}\\
        & \leq e^{(\frac{\epsilon k}{2 S(x)} + \ln 2)} \hexpmechPr{\dataobs}{\ux{z} = ( \ux{r} + k)}\\
        & = RHS.
        \end{split}
        \end{equation*}

>>>>

Let $\ux{t} = \ux{r} + k$. The proof is given by cases:
\begin{itemize}
  \item {\boldmath$\ux{r} \neq 0$, $\ux{r} + k \neq 0$}. \todo{$r \in \mathcal{R}_2 \land t \in \mathcal{R}_2$} \\
  By $\ux{r} + k \neq 0$, $\cardinality{\dataobs}{t} = 2$. \todo{By $t \in \mathcal{R}_2$, $\cardinality{\dataobs}{t} = 2$}\\
  By $\ux{r} \neq 0 $, $\cardinality{\dataobs}{r} = 2$. \todo{By $r \in \mathcal{R}_2$, $\cardinality{\dataobs}{r} = 2$}\\
  Destruct k:
  \begin{itemize}
    \item  $k \geq 0$: $\implies$\\
      \begin{equation*}
      \begin{split}
      LHS 
      & = \cardinality{\dataobs}{r} \cdot \hexpmechPr{\dataobs}{z = r}     (Apply\ Lemma\ \ref{lem_score_pro_convert})\\
      & = \cardinality{\dataobs}{r} \cdot \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}} 
      (Apply\ Definition\ \ref{def_smoo})\\
      & = \cardinality{\dataobs}{r} \cdot \frac{exp(\frac{-\epsilon \ux{r}}{2 S(\dataobs)})}{\unomalizer{\dataobs}}
      (Apply\ \ux{r} = \hellinger(\bysinfer(\dataobs), r))\\
      & = 2 \cdot \frac{exp(\frac{-\epsilon \ux{r}}{2 S(\dataobs)})}{\unomalizer{\dataobs}}                  (Apply\ \cardinality{\dataobs}{r} = 2)\\
      & = 2 \cdot \frac{exp(\frac{-\epsilon (\ux{r} + k - k)}{2 S(\dataobs)})}{\unomalizer{\dataobs}}\\
      & = 2 \cdot \frac{exp(\frac{-\epsilon (\ux{r} + k)}{2 S(\dataobs)} + \frac{\epsilon k}{2 S(\dataobs)})}{\unomalizer{\dataobs}}\\
      & = 2 \cdot \frac{exp(\frac{-\epsilon (\ux{r} + k)}{2 S(\dataobs)})}{\unomalizer{\dataobs}} \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}}\\
      & = 2 \cdot \frac{exp(\frac{-\epsilon (\ux{t})}{2 S(\dataobs)})}{\unomalizer{\dataobs}} \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}}  (Apply \ \ux{t} = \ux{r} + k)\\
      & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot 2 \cdot \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs), t)}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}} 
      (Apply\ \ux{r} = \hellinger(\bysinfer(\dataobs), r))\\
      & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot 2 \cdot \hexpmechPr{\dataobs}{z = t}       (Apply\ Definition\ \ref{def_smoo})\\
      & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \cardinality{\dataobs}{t} \cdot \hexpmechPr{\dataobs}{z = t}         (Apply \ \cardinality{\dataobs}{t} = 2)\\
      & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{\ux{z} = \ux{t}}               (Apply \ Lemma\ \ref{lem_score_pro_convert})\\
      & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{\ux{z} = (\ux{r} + k)}         (Apply \ \ux{t} = \ux{r} + k)\\
      & \leq e^{(\frac{\epsilon k}{2 S(\dataobs)} + \ln 2)} \cdot \hexpmechPr{\dataobs}{\ux{z} = (\ux{r} + k)}\\
      & = RHS.
      \end{split}
      \end{equation*}

@@

      \begin{equation*}
      \begin{split}
      LHS 
      & = \cardinality{\dataobs}{r} \cdot \hexpmechPr{\dataobs}{z = r}     (Apply\ Lemma\ \ref{lem_score_pro_convert})\\
      & = \cardinality{\dataobs}{r} \cdot \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}} 
      (Apply\ Definition\ \ref{def_smoo})\\
      & = \cardinality{\dataobs}{r} \cdot \frac{exp(\frac{-\epsilon \ux{r}}{2 S(\dataobs)})}{\unomalizer{\dataobs}}
      (Apply\ \ux{r} = \hellinger(\bysinfer(\dataobs), r))\\
      & = 2 \cdot \frac{exp(\frac{-\epsilon \ux{r}}{2 S(\dataobs)})}{\unomalizer{\dataobs}}                  (Apply\ \cardinality{\dataobs}{r} = 2)\\
      & = 2 \cdot \frac{exp(\frac{-\epsilon (\ux{r} + k - k)}{2 S(\dataobs)})}{\unomalizer{\dataobs}}\\
      & = 2 \cdot \frac{exp(\frac{-\epsilon (\ux{r} + k)}{2 S(\dataobs)} + \frac{\epsilon k}{2 S(\dataobs)})}{\unomalizer{\dataobs}}\\
      & = 2 \cdot \frac{exp(\frac{-\epsilon (\ux{r} + k)}{2 S(\dataobs)})}{\unomalizer{\dataobs}} \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}}\\
      & = 2 \cdot \frac{exp(\frac{-\epsilon (\ux{t})}{2 S(\dataobs)})}{\unomalizer{\dataobs}} \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}}  (Apply \ \ux{t} = \ux{r} + k)\\
      & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot 2 \cdot \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs), t)}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}} 
      (Apply\ \ux{r} = \hellinger(\bysinfer(\dataobs), r))\\
      & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot 2 \cdot \hexpmechPr{\dataobs}{z = t}       (Apply\ Definition\ \ref{def_smoo})\\
      & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \cardinality{\dataobs}{t} \cdot \hexpmechPr{\dataobs}{z = t}         (Apply \ \cardinality{\dataobs}{t} = 2)\\
      & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{\ux{z} = \ux{t}}               (Apply \ Lemma\ \ref{lem_score_pro_convert})\\
      & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{\ux{z} = (\ux{r} + k)}         (Apply \ \ux{t} = \ux{r} + k)\\
      & \leq e^{(\frac{\epsilon k}{2 S(\dataobs)} + \ln 2)} \cdot \hexpmechPr{\dataobs}{\ux{z} = (\ux{r} + k)}\\
      & = RHS.
      \end{split}
      \end{equation*}

@@

  \item {\boldmath$\ux{r} = 0, \ux{r} + k \neq 0$}. \todo{$r \in \mathcal{R}_1 \land t \in \mathcal{R}_2$}\\
        By $\ux{r} = 0$, $\cardinality{\dataobs}{r} = 1$. \todo{By $r \in \mathcal{R}_1$, $\cardinality{\dataobs}{t} = 1$}\\
        By $\ux{r} + k = k \neq 0$, $\cardinality{\dataobs}{t} = 2$. \todo{By $t \in \mathcal{R}_2$, $\cardinality{\dataobs}{t} = 2$}\\
        $\implies$\\
        \begin{equation*}
        \begin{split}
        LHS 
        & = \cardinality{\dataobs}{r} \cdot \hexpmechPr{\dataobs}{z = r}     (Apply\ Lemma\ \ref{lem_score_pro_convert})\\
        & = \cardinality{\dataobs}{r} \cdot \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}} 
        (Apply\ Definition\ \ref{def_smoo})\\
        & = \cardinality{\dataobs}{r} \cdot \frac{exp(\frac{-\epsilon \ux{r}}{2 S(\dataobs)})}{\unomalizer{\dataobs}}
        (Apply\ \ux{r} = \hellinger(\bysinfer(\dataobs), r))\\
        & = \frac{exp(\frac{- \epsilon \ux{r}}{2 S(\dataobs)})}{\unomalizer{\dataobs}}                        (Apply \ \cardinality{\dataobs}{r} = 1) \\
        & = \frac{exp(\frac{- \epsilon (\ux{r} + k - k)}{2 S(\dataobs)})}{\unomalizer{\dataobs}}\\
        & = \frac{exp(\frac{- \epsilon (\ux{r} + k)}{2 S(\dataobs)} + \frac{\epsilon k}{2 S(\dataobs)})}{\unomalizer{\dataobs}}\\
        & = \frac{exp(\frac{-\epsilon (\ux{r} + k)}{2 S(\dataobs)})}{\unomalizer{\dataobs}} \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}}\\
        & = \frac{exp(\frac{-\epsilon (\ux{t})}{2 S(\dataobs)})}{\unomalizer{\dataobs}} \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}}  (Apply \ \ux{t} = \ux{r} + k)\\
        & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs), t)}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}} 
        (Apply\ \ux{r} = \hellinger(\bysinfer(\dataobs), r))\\
        & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{z = t}       (Apply\ Definition\ \ref{def_smoo})\\
        & < 2 \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{z = t}\\
        & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \cardinality{\dataobs}{t} \cdot \hexpmechPr{\dataobs}{z = t}   (Apply \ \cardinality{\dataobs}{t} = 2)\\
        & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{\ux{z} = \ux{t}}         (Apply \ Lemma\ \ref{lem_score_pro_convert})\\
        & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{\ux{z} = (\ux{r} + k)}   (Apply \ \ux{t} = \ux{r} + k)\\
        & \leq e^{(\frac{\epsilon k}{2 S(\dataobs)} + \ln 2)} \cdot \hexpmechPr{\dataobs}{\ux{z} = ( \ux{r} + k)}\\
        & = RHS.
        \end{split}
        \end{equation*}

@@

      $\implies$
      \begin{equation*}
      \begin{split}
      LHS   
      & = \cardinality{\dataobs}{r} \cdot \hexpmechPr{\dataobs}{z = r}     (Apply\ Lemma\ \ref{lem_score_pro_convert})\\
      & = \cardinality{\dataobs}{r} \cdot \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}} 
      (Apply\ Definition\ \ref{def_smoo})\\
      & = \cardinality{\dataobs}{r} \cdot \frac{exp(\frac{-\epsilon \ux{r}}{2 S(\dataobs)})}{\unomalizer{\dataobs}}
      (Apply\ \ux{r} = \hellinger(\bysinfer(\dataobs), r))\\
      & = 2 \cdot \frac{exp(\frac{-\epsilon \ux{r}}{2 S(\dataobs)})}{\unomalizer{\dataobs}}                  (Apply \ \cardinality{\dataobs}{r} = 2)\\
      & = 2 \cdot \frac{exp(\frac{-\epsilon (\ux{r} + k - k)}{2 S(\dataobs)})}{\unomalizer{\dataobs}}\\
      & = 2 \cdot \frac{exp(\frac{-\epsilon (\ux{r} + k)}{2 S(\dataobs)} + \frac{\epsilon k}{2 S(\dataobs)})}{\unomalizer{\dataobs}}\\
      & = 2 \cdot \frac{exp(\frac{-\epsilon (\ux{r} + k)}{2 S(\dataobs)})}{\unomalizer{\dataobs}} \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}}\\
      & = 2 \cdot \frac{exp(\frac{-\epsilon (\ux{t})}{2 S(\dataobs)})}{\unomalizer{\dataobs}} \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}}  (Apply \ \ux{t} = \ux{r} + k)\\
      & = 2 \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs), t)}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}} 
      (Apply\ \ux{r} = \hellinger(\bysinfer(\dataobs), r))\\
      & = 2 \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}} \hexpmechPr{\dataobs}{z = t}       (Apply\ Definition\ \ref{def_smoo})\\
      & = 2 \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \cardinality{\dataobs}{t} \cdot \hexpmechPr{\dataobs}{z = t} (Apply\ \cardinality{\dataobs}{t} = 1)\\
      & = 2 \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{\ux{z} = \ux{t}}       (Apply \ Lemma\ \ref{lem_score_pro_convert})\\
      & = 2 \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{\ux{z} = (\ux{r} + k)} (Apply \ \ux{t} = \ux{r} + k)\\
      & = e^{\ln 2} \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{\ux{z} = (\ux{r} + k)}\\
      & = e^{(\frac{\epsilon k}{2 S(\dataobs)} + \ln 2)} \cdot \hexpmechPr{\dataobs}{\ux{z} = (\ux{r} + k)}\\
      & = RHS.
      \end{split}
      \end{equation*}

@@

        \begin{equation*}
        \begin{split}
        LHS 
        & = \hexpmechPr{\dataobs}{\ux{z} = \ux{r} + 0}\\
        & = \hexpmechPr{\dataobs}{\ux{z} = \ux{r} + k}\\
        & \leq e^{(\frac{\epsilon k}{2 S(x)} + \ln 2)} \cdot \hexpmechPr{\dataobs}{\ux{z} = ( \ux{r} + k)}\\
        & = RHS.
        \end{split}
        \end{equation*}
